\title{Ankit-Tayal}
\author{Ankit Tayal}
\date{October 2024}
\documentclass[10pt]{extarticle}
\usepackage[margin=0.2in]{geometry}
\usepackage{romannum}
\usepackage[most]{tcolorbox}
\usepackage{enumitem}
\usepackage{multicol}
\usepackage[hidelinks]{hyperref}
\setlist[itemize]{noitemsep, topsep=0pt}
\addtolength{\parskip}{-1.5mm}
\pdfgentounicode=1


\tcbset{
    frame code={}
    center title,
    left=0pt,
    right=0pt,
    top=0pt,
    bottom=0pt,
    colback=gray!20,
    colframe=white,
    width=\dimexpr\textwidth\relax,
    enlarge left by=0mm,
    boxsep=3pt,
    arc=0pt,outer arc=0pt,
}
\begin{document}

\begin{center}
\noindent {\huge\textbf{Ankit Tayal}}
\end{center}

\noindent \textbf{Github:} \href{https://github.com/ankitT20/}{\color{blue}ankitT20} \hfill 
\textbf{Email:}  \href{mailto:tayalankit20@icloud.com}{tayalankit20@icloud.com} \\
\textbf{LinkedIn:} \href{https://www.linkedin.com/in/ankit-tayal-ip/}{\color{blue}ankit-tayal-ip}\hfill \textbf{Phone:} +91-9953301972
\vspace{-6pt}
\\
\vspace{-10pt}
\noindent\rule[0.5ex]{\linewidth}{1pt}
{\large \textbf{\begin{tcolorbox}\textsc{Education}\end{tcolorbox}}}
\vspace{-10pt}
\begin{center}
% \begin{tabular}{|p{2.5cm}|p{6.0cm}|p{8.0cm}|p{1.8cm}|}
\begin{tabular}{|p{2.5cm}|p{6.0cm}|p{8.5cm}|p{1.8cm}|}
\hline
\centering{\textbf{Year}} & \centering{\textbf{Degree/Board}} & \centering{\textbf{Institute}} & \textbf{CGPA/$\%$}\\
\hline
% Jun 2021 - Jun 2025
\centering{Jun 2025} & \centering{B.Tech in Industrial Internet of Things} & \centering{University School of Automation and Robotics, GGSIPU, New Delhi} & 8/10\\
\hline
\centering{Apr 2021} & \centering{CBSE (\Romannum{12})} & \centering{Lancer’s Convent, New Delhi} & 81\%\\
\hline
\centering{Apr 2019} & \centering{CBSE (\Romannum{10})} & \centering{Lancer’s Convent, New Delhi} & 78\%\\
\hline
\end{tabular}
\end{center}

\vspace{-10pt}
{\large \textbf{\begin{tcolorbox}\textsc{Work Experience}\end{tcolorbox}}}
\vspace{-5pt}
\begin{itemize}
    \item \textbf{Co-Lead in Cloud Computing and Founding Member} \hfill (\textit{Aug 2023 - Aug 2024})\\
    \textbf{Google Developer Student Club USAR} \hfill Delhi, India
    % $|$ \textit{\href{https://n0c.tech/} {\color{blue}{Link}}}
    \begin{itemize}
        \item Organized and executed a successful \textbf{Google Cloud Study Jam event}, resulting in achieving Tier 1 status and \textbf{providing all 80 students with valuable goodies}, including a \textbf{Google Cloud certificate}, bag, t-shirt, bottle, and stickers.
        \item Secured industry expert JKGunnink as a keynote speaker for multiple events to secure speaking engagements for cloud computing events, \textbf{increasing attendance by 300\%} and enhancing the overall experience for participants.
        \item \textbf{Led the founding of} the Google Developer Student Club at the university, growing membership to over \textbf{120 active participants} within the first semester of inception.
    \end{itemize}
    \item \textbf{Financial Research Analyst} \hfill (\textit{Aug 2022 - Dec 2022})\\
    \textbf{Assetgro Fintech Pvt. Ltd. (StockGro)} \hfill Delhi, India
    \begin{itemize}
        \item Enhanced customer engagement by revamping \textbf{live information} sections, leading to a \textbf{15\% increase in subscription sales} and retention rates.
        \item Analyzed and \textbf{interpreted data on Nifty stocks to identify trends} and opportunities, resulting in a 10\% increase in successful investment decisions.
        \item Utilized equity research analysis skills to provide detailed financial reporting and stock market analysis, contributing to a \textbf{20\% improvement in overall portfolio} performance.
    \end{itemize}
\end{itemize}

\vspace{-10pt}\vspace{-5pt}
{\large \textbf{\begin{tcolorbox}\textsc{Projects}\end{tcolorbox}}}
\vspace{-5pt}
\begin{itemize}
    \item \textbf{Signature Authentication} $|$ \textit{Numpy, OpenCV, TensorFlow, Keras, SkLearn, Matplotlib} $|$ \textit{\href{https://github.com/ankitT20/SignatureAuth} {\color{blue}{GitHub}}}
    \begin{itemize}
        \item Applied advanced preprocessing techniques such as resizing, normalization, and data augmentation using \textbf{NumPy} and \textbf{OpenCV} to optimize signature data sets.
        \item Designed and fine-tuned deep learning models, including Shallow \textbf{CNN}, \textbf{ResNet}, and \textbf{Siamese Network}, using \textbf{TensorFlow} and \textbf{Keras}, achieving exceptional accuracy on BHSig260 and Cedar datasets.
        % \item Created a robust system for \textbf{forgery detection} in handwritten signatures, significantly enhancing \textbf{verification efficiency by 50\%}. Evaluated model performance using ROC Curves, Confusion Matrix, Accuracy and Loss Curves with \textbf{SkLearn} and \textbf{Matplotlib}.
        \item Created a robust system for \textbf{forgery detection} in handwritten signatures, enhancing \textbf{verification efficiency by 50\%}. Evaluated model performance using ROC Curves, Confusion Matrix, Accuracy and Loss Curves with \textbf{SkLearn}, \textbf{Matplotlib}.
        % remove [significantly, and] to get one line extra 
    \end{itemize}
    
    \item \textbf{Unified Academic Services Platform} $|$ \textit{HTML, CSS3, React.js, RapidAPI, Java Script} $|$ \textit{\href{https://github.com/ankitT20/UASP} {\color{blue}{GitHub}}}
    \begin{itemize}
        \item Developed web-based \textbf{Learning Management System} using \textbf{Python}, Django, \textbf{PostgreSQL}, HTML, SCSS, \textbf{JavaScript}.
        \item Implemented multilingual support and integrated third party services like Stripe with \textbf{Celery} and \textbf{Redis} for efficient background task processing, ensuring a \textbf{scalable} and \textbf{user-friendly} platform for both students and faculty, streamlining course management, quizzes, payments, and result tracking for academic institutions.
        \item Utilized \textbf{Agile methodology} with \textbf{Jira} for task management, resulting in a 30\% increase in team productivity. Deployed a high availability system on \textbf{AWS Ubuntu Server}, focused on \textbf{real-time updates}, role-based access, secure authentication.
  \end{itemize}

      \item \textbf{Risk analysis of portfolio} $|$ \textit{Python, Scipy, Numpy, Pandas, Matplotlib} $|$ \textit{\href{https://github.com/ankitT20/Risk_analysis_Portfolio} {\color{blue}{GitHub}}}
    \begin{itemize}
         \item \textbf{Portfolio Optimization}: Developed a model to maximize portfolio return considering covariance matrix and investment constraints, using \textbf{Python} for \textbf{data analysis} and optimization.
        \item \textbf{Risk Analysis Tools}: Assessed statistical tools like Mean Absolute Deviation (MAD) and Conditional Value at Risk (CVaR) to measure and analyze investment risks.
  \end{itemize}
    
    % \item \textbf{Drona (AI-Aim Trainer)} $|$ \textit{OpenCV, Mediapipe, Django} $|$ \textit{\href{https://github.com/Ankitkej9/Aim-Tracker}{\color{blue}{GitHub}}}
    % % \vspace{-5pt}
    
    % \begin{itemize}
    %     \item Developed during the MLH Hackathon, this project trains aim skills by shooting objects through eye movement.
    %     \item Reconstructed an open-source Aim Game, by integrating eye control using \textbf{OpenCV} and \textbf{MediaPipe}.
    %     \item Built and deployed the backend with Signin, Signup, Logout, and User profile features using \textbf{Django}.
    % \end{itemize}
\end{itemize}

\vspace{-15pt}
{\large \textbf{\begin{tcolorbox}\textsc{Technical Skills}\end{tcolorbox}}}
\vspace{-7pt}
\begin{itemize}
    \item \textbf{Programming Languages:} Java 8, C/C++, Python, JavaScript, SQL.
    \item \textbf{Technologies:} Amazon AWS, React.js, Next.js, Express.js, Node.js, HTML, CSS3, MySQL, WordPress, Matplotlib, Numpy, Pandas, Tensorflow, Selenium, Machine Learning, Deep Learning, Docker, DevOps, Azure, GCP.
    \item \textbf{Coursework:} Data Structures Algorithms, Object-Oriented Programming, Operating Systems, Database Management System.
    \item \textbf{Tools:} Postman, VScode, Git, Linux, Spring Boot, JWT, Kafka, ELK, Collection Framework, caching, Elastic Search, Java SE
\end{itemize}
\vspace{-10pt}
{\large \textbf{\begin{tcolorbox}\textsc{Achievements}\end{tcolorbox}}}
\vspace{-7pt}
\begin{itemize}
    \item \emph{\href{https://github.com/ankitT20/Achievements/blob/main/Cert/IBM_Data_Analytics_Summer_Internship_Certificate.pdf}{\color{blue}Internship Certificate}}: Completed a 6-week \textbf{IBM} SkillsBuild \textbf{Summer Internship} Program in \textbf{Data Analytics} with CSRBOX.
    \item \emph{\href{https://github.com/ankitT20/Achievements/blob/main/Cert/IIT_Delhi_Merit_Certificate_Rendezvous.pdf}{\color{blue}Merit Certificate}}:\textbf{ 1st Rank} in CryptoCon \textbf{IIT Delhi}{, Achieved 1st place in CryptoCon, a 5-day trading event at IIT Delhi's annual cultural fest, Rendezvous 2022, winning a cash prize and goodies.}
    \item Solved over 200 problems in Data Structures and Algorithms on platforms like Pepcoding.
    % \href{https://leetcode.com/u/Ankitkej9/}{\textbf{LeetCode}}, \href{https://www.geeksforgeeks.org/user/Ankitkejri9/}{\textbf{GeeksforGeeks}}, \href{https://www.naukri.com/code360/profile/0df7a435-3893-4e8e-b617-adbe1e356bf3}{\textbf{Codestudio}}.
    \item Ranked 5th in department during 2nd semester.
\end{itemize}
\end{document}
